---
title: "Iteration and List Columns"
author: "Shumei Liu"
date: "2024-11-14"
output: github_document
---

```{r}
library(tidyverse)
library(rvest)
```

## Lists

You can put anything in a list.

```{r}
vec_numeric = 5:8
vec_char = c("My", "name", "is", "Jeff")
vec_logical = c(TRUE, TRUE, TRUE, FALSE)
```

```{r}
l = list(
  vec_numeric = 5:8,
  mat         = matrix(1:8, 2, 4),
  vec_logical = c(TRUE, FALSE),
  summary     = summary(rnorm(1000)))
l
```

```{r}
l$vec_numeric

l[[1]]

l[[1]][1:3]

mean(l[["vec_numeric"]])
```

## `for` loop

Create a new list.

```{r}
list_norms = 
  list(
    a = rnorm(20, 3, 1),
    b = rnorm(20, 0, 5),
    c = rnorm(20, 10, .2),
    d = rnorm(20, -3, 1)
  )

is.list(list_norms)
```

Pause and get the old function.

```{r}
mean_and_sd = function(x) {
  
  if (!is.numeric(x)) {
    stop("Argument x should be numeric")
  } else if (length(x) == 1) {
    stop("Cannot be computed for length 1 vectors")
  }
  
  mean_x = mean(x)
  sd_x = sd(x)

  tibble(
    mean = mean_x, 
    sd = sd_x
  )
}
```

I can apply that function to each list element.

```{r}
mean_and_sd(list_norms[[1]])

mean_and_sd(list_norms[[2]])

mean_and_sd(list_norms[[3]])

mean_and_sd(list_norms[[4]])
```

Let's use a `for` loop.

```{r}
output = vector("list", length = 4)

for (i in 1:4) {
  output[[i]] = mean_and_sd(list_norms[[i]])
}

output
```

## `map`

```{r}
output = map(list_norms, mean_and_sd) #list_norms to keep the name of each distribution

output
```

what if you want a different function?

```{r}
output = map(list_norms, median)

output
```

## `map` variants变体

```{r}
output = map_dbl(list_norms, median, .id = "input")

output
```
We use `map_dbl` because median outputs a single numeric value each time; the result is a vector instead of a list. Using the `.id` argument keeps the names of the elements in the input list.

If we tried to use `map_int` or `map_lgl`, we’d get an error because the output of median isn’t a integer or a logical.

```{r}
output = map_dfr(list_norms, mean_and_sd, .id = "input") 

output
```





